Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-18 doc/manuscript_hkk_drought_sensitivity.Rmd
keywords and data accessibility

# Keywords {-}

@@

# Data Accessibility Statement {-}

>>>>

# Keywords {-}
drought response, tree growth, tropical forest, microenvironment buffering, deciduousness

@@

# Data Accessibility Statement {-}
This manuscript does not use novel code. 
The dendrometer band data used for this manuscript is archived in the ForestGEO data repository and will be made available upon request. 
The climate data used in this work are publicly available. 
The code used to analyse the data will be made available in Zenodo upon acceptance of the manuscript.
